---
title: "A UN report on the Relationship between GDP and Life Expectancy and CO2 emissions"
author: "Manuela Alvarado Obando"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(tidyverse)
library(ggprism)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r read-data}
gapminder_1997<-read_csv("data/gapminder_1997.csv")

```
```{r gdp-lifeExp-1997-plot}
#make plot of GDP vs lifeExp
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, color = continent) +
  geom_point() +
  labs(x = "GDP per Capita", y = "Life Expectancy (yrs)") +
  theme_prism()
```

